The problem and promise of scale in multilayer networks

### 2020-01-28 paper/manuscript.Rmd
blah

![**Figure 1**](../graphics/figure1.png) 
**Figure 1**: Space-time diagram displaying variation the spatial and temporal extent required for different social processes across a range of taxa.
\clearpage

>>>>

![**Figure 1**](../graphics/figure1.png)

**Figure 1**: Space-time diagram displaying variation the spatial and temporal extent required for different social processes across a range of taxa.
\clearpage
